EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Added some examples to try to answer the question 'why coverage decreased in some cases with higher time budget?'.

% Look at benchmarks where coverage decreased with increased budget
Although coverage generally increased with higher time budgets, there
are instances where this expected behaviour was not observed,
specially for $budget=300s$, where the average across benchmarks
decreased. This is possibly due to crashes or out-of-memory
runtime errors.\TODO{confirm this conjecture}\TODO{look into details}

>>>>

% Look at benchmarks where coverage decreased with increased budget
Although coverage generally increased with higher time budgets, there
are instances where this expected behaviour was not observed,
specially for $budget=300s$, where the average across benchmarks
decreased. This is possibly due to crashes or out-of-memory runtime
errors. For instance, \EVOSUITE failed to generate any test suite in
one out of three runs of OKHTTP-2 and RE2J-7 due to an
\textit{out-of-memory error}, and in all executions of LA4J-3 and
LA4J-7 due to a \textit{state exception}. In order to evaluate a
fitness function, each test case evolved by the underline GA of
\EVOSUITE has to be executed. However, its execution could fail due to
several reasons: state exception (if a test case tries to re-initalize
EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
case of a timeout, \EVOSUITE logs the stacktrace of the thread in
which each test case is executed, which could cause an out-of-memory
error if the stack trace message is to long. RE2J-7: \TODO{I do not
understand how a java.lang.OutOfMemoryError could be throw by
CBranchSuiteFitness.java:145}.
%
To avoid low coverage of final classes with private constructors (like
the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
to call the default constructor of the class under test. However,
\TODO{EvoSuite tries to access a field of the cut (which is public
static final) by using an instance of cut. It's still not clear why}.
For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
\EVOSUITE failed due to mocking related issues.
